---
title: "Expected [X] Template"
output:
  rmdformats::material:
    highlight: kate
    self_contained: true
    code_folding: show
    thumbnails: true
    gallery: true
    fig_width: 4
    fig_height: 4
    css: styles.css
---

```{r knitr_init, echo=FALSE, cache=FALSE}
library(knitr)
library(rmdformats)

## Global options
options(max.print = "75")
opts_chunk$set(echo = TRUE,
	             cache = TRUE,
               prompt = FALSE,
               tidy = TRUE,
               comment = NA,
               message = FALSE,
               warning = FALSE)
opts_knit$set(width = 75)
```

# Abstract
A paragraph summarizing the entire study, including a brief statement of the 
problem, the motivation, data soruces, analysis and results, and general 
conclusions.

# Introduction
Discussion of problem here, including motivation, underlying theory, etc...

## Data Sources
Discussion of data sources followed by a bullet list including ULRs, etc...

* **Data Sources**
    
# Data Processing
Discussion of general data processing strategy from sources.  Discussion of API
calls, imports, etc...

## Libraries
Discussion of required libraries.
```{r}
# Insert library calls here
```

## Reshape
Discussion of current data format and reshaping strategy.

```{r}
# Insert data reshaping code here
```

## Calculations
Discussion of some aggregate calculations to be made before data analysis, 
computing a yearly average for example.

```{r}
# Insert data calculation code here
```

# Analysis and Results
Discussion of general analysis strategy, for example, the kinds of models and 
techiques that will be utilized.  This section will likely contain many code 
chucks for both calculations and plots, below each of which sould be a 
discussion of the plot, table, code, etc...

```{r}
# Insert analysis code here.  Code may involve plots, tables, and values.
```

# Conclusions
Discussion of results, difficulties, and further investigation.